### 2024-09-16 texts/sup_materials.tex
minor polishing, update tasks, send email, update sups

% Created 2024-09-09 ma 12:03
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.4 (Org mode 9.7.9)}, 
 pdflang={English}}
\begin{document}

\section*{Supplementary online materials}

\subsection*{Alternative competition specifications}

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_heatmap_alt.pdf}
\caption{\label{fig:p_pred_heatmap_alt}Prediction Heatmap of Alternative model specifications}
\end{figure}

@@

\begin{landscape}
% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:47 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pmdens1} & \multicolumn{1}{l}{r\_pmdens2} & \multicolumn{1}{l}{r\_audience1} & \multicolumn{1}{l}{r\_audience\_log1}\\ 
 \hline
  \multicolumn{7}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & .00 \; (0.33) & -.05 \; (0.33) & -.00 \; (0.33) & -.11 \; (0.33) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.22 \; (0.32) & -.18 \; (0.32) & -.21 \; (0.32) & -.23 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .19 \; (0.43) & .25 \; (0.43) & .18 \; (0.43) & .08 \; (0.43) \\ 
   \multicolumn{7}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .36 \; (0.40) & .33 \; (0.40) & .37 \; (0.40) & .44 \; (0.40) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.09 \; (0.50) & -.20 \; (0.51) & -.05 \; (0.51) & .05 \; (0.51) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.03 \; (0.30)^{***} & 1.12 \; (0.31)^{***} & 1.05 \; (0.30)^{***} & 1.13 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .24 \; (0.34) & .17 \; (0.35) & .23 \; (0.34) & .18 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .45 \; (0.50) & .31 \; (0.50) & .45 \; (0.49) & .47 \; (0.49) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .10 \; (0.28) & .14 \; (0.28) & .10 \; (0.28) & .07 \; (0.28) \\ 
   \multicolumn{7}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .50 \; (0.32) & .41 \; (0.34) & .55 \; (0.33) & .73 \; (0.31)^{*} \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.03 \; (0.03) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  &  &  &  \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} &  &  &  &  \\ 
   & PM density (10km) &  & -.00 \; (0.03) &  &  &  \\ 
   & PM density (10km, log) &  &  & .29 \; (0.15) &  &  \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  &  &  &  \\ 
   & Local Audience per PM &  &  &  & .10 \; (0.14) &  \\ 
   & Local Audience per PM (log) &  &  &  &  & .28 \; (0.09)^{**} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.65 \; (1.01) & -1.64 \; (1.01) & -1.65 \; (1.01) & -1.63 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .44 \; (0.29) & .46 \; (0.29) & .43 \; (0.29) & .42 \; (0.29) \\ 
   \hline
 & Museums & 503 & 503 & 503 & 503 & 503 \\ 
   & Museum-years & 6096 & 6096 & 6096 & 6096 & 6096 \\ 
   & Closures & 68 & 68 & 68 & 68 & 68 \\ 
   & log. Likelihood & -339.68 & -347.93 & -346.18 & -347.72 & -342.93 \\ 
   & AIC & 711.35 & 723.85 & 720.35 & 723.44 & 713.86 \\ 
   & BIC & 746.87 & 754.93 & 751.42 & 754.51 & 744.93 \\ 
   \hline 
 \multicolumn{7}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Alternative specification of environment} 
\label{tbl:t_reg_coxph_env}
\end{table}
\end{landscape}

These while it would be possible for these different specifications to lead to similar interpretations, in practice they diverge substantially (table \ref{tbl:t_reg_coxph_env}).
Using Private museum density (model 2 and 3 for linear and log-transformed audience, figure \ref{fig:p_pred_heatmap_alt} bottom left), the general conclusion would be that (logged) competition increases mortality as predicted closing chance is highest in areas of low population and large private museum populations.
However, using audience (models 4 and 5, figure \ref{fig:p_pred_heatmap_alt} bottom right) leads to the opposite conclusion, as higher audience is associated with higher mortality; predicted closing chance is highest for areas of low numbers of private museums and large populations.
While it is beyond the scope of the paper to explore the origin of these diverging perspectives in detail, it is worth pointing out that the main specification of private interacted private museum and population counts captures both of these relationships, which arguably makes it preferable for its encompassingness.
\subsection*{Alternative sample specifications}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:39 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_onlycryside} & \multicolumn{1}{l}{r\_wocryside} & \multicolumn{1}{l}{r\_pop42}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & -1.07 \; (0.78) & .21 \; (0.44) & -.01 \; (0.34) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.27 \; (0.46) & .07 \; (0.52) & -.12 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .58 \; (0.59) & -.19 \; (0.77) & .29 \; (0.43) \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .31 \; (0.58) & 1.02 \; (0.65) & .18 \; (0.41) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -18.23 \; (4781.88) & .95 \; (0.71) & -.50 \; (0.55) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & .67 \; (0.46) & 1.95 \; (0.51)^{***} & 1.09 \; (0.31)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .55 \; (0.58) & -.32 \; (0.48) & .18 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & -.06 \; (0.85) & .18 \; (0.73) & .47 \; (0.50) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .24 \; (0.44) & -.30 \; (0.42) & .04 \; (0.28) \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .88 \; (0.44)^{*} & -1.16 \; (2.52) & .67 \; (0.34)^{*} \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.04 \; (0.02) & 1.33 \; (2.38) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & 1.69 \; (0.81)^{*} & .17 \; (0.17) & .20 \; (0.12) \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .64 \; (1.06) & .19 \; (0.10) & .22 \; (0.20) \\ 
   & Nbr PM$^{2}$ within 10km &  &  &  & .01 \; (0.02) \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.54 \; (1.83) & -.07 \; (0.04)^{*} & -.02 \; (0.09) \\ 
   & Nbr PM$^{2}$ (10km) * Pop (10km) &  &  &  & -.01 \; (0.01) \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -.75 \; (1.04) & -18.42 \; (5245.29) & -1.59 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .46 \; (0.47) & .30 \; (0.41) & .45 \; (0.29) \\ 
   \hline
 & Museums & 503 & 283 & 219 & 503 \\ 
   & Museum-years & 6096 & 3311 & 2265 & 6096 \\ 
   & Closures & 68 & 28 & 35 & 68 \\ 
   & log. Likelihood & -339.68 & -116.47 & -139.36 & -338.79 \\ 
   & AIC & 711.35 & 264.94 & 310.72 & 713.59 \\ 
   & BIC & 746.87 & 286.25 & 335.60 & 753.54 \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH models of different local density specifications} 
\label{tbl:t_reg_coxph_density}
\end{table}

To investigate the robustness of the coefficients across different values, table \ref{tbl:t_reg_coxph_density} shows how coefficients according to sample restrictions. 
In model 1, only museums are included which are located in areas with the highest value combination of number and private museums and population, i.e. museums located in an environment of less than 2 million people and 0 or 1 other private museums (the "countryside").
In model 2, the "countryside" is excluded.
However, both these models are not reliable, as they do not properly converge (indicated by extremely large coefficients in both models).
\subsection*{Alternative time range specifications}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_2005} & \multicolumn{1}{l}{r\_2010} & \multicolumn{1}{l}{r\_2015}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & .00 \; (0.34) & .05 \; (0.34) & .31 \; (0.37) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.10 \; (0.32) & -.39 \; (0.35) & -.35 \; (0.40) \\ 
   & Founder died & .28 \; (0.43) & .13 \; (0.46) & .34 \; (0.46) & -.22 \; (0.55) \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .25 \; (0.42) & .24 \; (0.43) & -.13 \; (0.48) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.41 \; (0.54) & -.37 \; (0.55) & -.62 \; (0.60) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.14 \; (0.31)^{***} & 1.15 \; (0.32)^{***} & .96 \; (0.35)^{**} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .17 \; (0.34) & .26 \; (0.35) & -.35 \; (0.49) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .22 \; (0.55) & .28 \; (0.55) & .13 \; (0.56) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .05 \; (0.28) & -.01 \; (0.29) & .46 \; (0.32) \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .70 \; (0.38) & .40 \; (0.45) & .25 \; (0.51) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) & -.02 \; (0.03) & -.02 \; (0.06) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} & .25 \; (0.10)^{**} & .24 \; (0.11)^{*} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .25 \; (0.08)^{***} & .25 \; (0.08)^{***} & .23 \; (0.08)^{**} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.07 \; (0.03)^{*} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.69 \; (1.01) &  &  \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .33 \; (0.29) & .28 \; (0.30) & .12 \; (0.31) \\ 
   \hline
 & Museums & 503 & 502 & 499 & 485 \\ 
   & Museum-years & 6096 & 5483 & 4474 & 2901 \\ 
   & Closures & 68 & 67 & 64 & 50 \\ 
   & log. Likelihood & -339.68 & -329.47 & -304.28 & -217.32 \\ 
   & AIC & 711.35 & 690.94 & 638.57 & 464.65 \\ 
   & BIC & 746.87 & 726.22 & 670.95 & 493.33 \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH regression results with different time slices} 
\label{tbl:t_reg_coxph_timeslice}
\end{table}

Table \ref{tbl:t_reg_coxph_timeslice} investigates whether relationships have substantially changed over time.
However, subsetting the dataset to different year ranges shows general consistency of the main findings, in particular insignificant coefficients for the founder's death, gender, Artnews ranking variables, inclusion of founder name in museum name, positive and significant coefficients for self-identification as other, population and private museum numbers, and a significant negative interaction between private museum numbers and population.
\subsection*{Inclusion of Exhibition data}

>>>>

% Created 2024-09-11 wo 13:29
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes Aengenheyster}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes Aengenheyster},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.4 (Org mode 9.7.9)}, 
 pdflang={English}}
\begin{document}

\section*{Supplementary online materials}
\label{sec:orgb29274c}

\subsection*{Alternative competition specifications}
\label{sec:org52f01e9}

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_heatmap_alt.png}
\caption{\label{fig:p_pred_heatmap_alt}Prediction Heatmap of Alternative model specifications}
\end{figure}

@@

\begin{landscape}
% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:47 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}llllll}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pmdens1} & \multicolumn{1}{l}{r\_pmdens2} & \multicolumn{1}{l}{r\_audience1} & \multicolumn{1}{l}{r\_audience\_log1}\\ 
 \hline
  \multicolumn{7}{l}{\textbf{Founder}} \\ 
 & Gender - Female & $-.04 \; (0.34)$ & $.00 \; (0.33)$ & $-.05 \; (0.33)$ & $-.00 \; (0.33)$ & $-.11 \; (0.33)$ \\ 
   & Gender - Couple & $-.14 \; (0.32)$ & $-.22 \; (0.32)$ & $-.18 \; (0.32)$ & $-.21 \; (0.32)$ & $-.23 \; (0.32)$ \\ 
   & Founder died & $.28 \; (0.43)$ & $.19 \; (0.43)$ & $.25 \; (0.43)$ & $.18 \; (0.43)$ & $.08 \; (0.43)$ \\ 
   \multicolumn{7}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & $.20 \; (0.41)$ & $.36 \; (0.40)$ & $.33 \; (0.40)$ & $.37 \; (0.40)$ & $.44 \; (0.40)$ \\ 
   & Self-Identification - Collection & $-.45 \; (0.54)$ & $-.09 \; (0.50)$ & $-.20 \; (0.51)$ & $-.05 \; (0.51)$ & $.05 \; (0.51)$ \\ 
   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ & $1.03 \; (0.30)^{***}$ & $1.12 \; (0.31)^{***}$ & $1.05 \; (0.30)^{***}$ & $1.13 \; (0.30)^{***}$ \\ 
   & AN Ranking - Included & $.19 \; (0.34)$ & $.24 \; (0.34)$ & $.17 \; (0.35)$ & $.23 \; (0.34)$ & $.18 \; (0.34)$ \\ 
   & AN Ranking - Dropped & $.46 \; (0.50)$ & $.45 \; (0.50)$ & $.31 \; (0.50)$ & $.45 \; (0.49)$ & $.47 \; (0.49)$ \\ 
   & Founder name in Museum name & $.05 \; (0.28)$ & $.10 \; (0.28)$ & $.14 \; (0.28)$ & $.10 \; (0.28)$ & $.07 \; (0.28)$ \\ 
   \multicolumn{7}{l}{\textbf{Environment}} \\ 
 & PM density (country) & $.65 \; (0.34)$ & $.50 \; (0.32)$ & $.41 \; (0.34)$ & $.55 \; (0.33)$ & $.73 \; (0.31)^{*}$ \\ 
   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ & $-.02 \; (0.02)$ & $-.02 \; (0.02)$ & $-.02 \; (0.02)$ & $-.03 \; (0.03)$ \\ 
   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ & $NA$ & $NA$ & $NA$ & $NA$ \\ 
   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ & $NA$ & $NA$ & $NA$ & $NA$ \\ 
   & PM density (10km) & $NA$ & $-.00 \; (0.03)$ & $NA$ & $NA$ & $NA$ \\ 
   & PM density (10km, log) & $NA$ & $NA$ & $.29 \; (0.15)$ & $NA$ & $NA$ \\ 
   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ & $NA$ & $NA$ & $NA$ & $NA$ \\ 
   & Local Audience per PM & $NA$ & $NA$ & $NA$ & $.10 \; (0.14)$ & $NA$ \\ 
   & Local Audience per PM (log) & $NA$ & $NA$ & $NA$ & $NA$ & $.28 \; (0.09)^{**}$ \\ 
   & Great Recession (2008/09) & $-1.59 \; (1.01)$ & $-1.65 \; (1.01)$ & $-1.64 \; (1.01)$ & $-1.65 \; (1.01)$ & $-1.63 \; (1.01)$ \\ 
   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ & $.44 \; (0.29)$ & $.46 \; (0.29)$ & $.43 \; (0.29)$ & $.42 \; (0.29)$ \\ 
   \hline
 & Museums & $503$ & $503$ & $503$ & $503$ & $503$ \\ 
   & Museum-years & $6096$ & $6096$ & $6096$ & $6096$ & $6096$ \\ 
   & Closures & $68$ & $68$ & $68$ & $68$ & $68$ \\ 
   & log. Likelihood & $-339.68$ & $-347.93$ & $-346.18$ & $-347.72$ & $-342.93$ \\ 
   & AIC & $711.35$ & $723.85$ & $720.35$ & $723.44$ & $713.86$ \\ 
   & BIC & $746.87$ & $754.93$ & $751.42$ & $754.51$ & $744.93$ \\ 
   \hline 
 \multicolumn{7}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Alternative specification of environment} 
\label{tbl:t_reg_coxph_env}
\end{table}
\end{landscape}

These while it would be possible for these different specifications to lead to similar interpretations, in practice they diverge substantially (table \ref{tbl:t_reg_coxph_env}).
Using Private museum density (model 2 and 3 for linear and log-transformed audience, figure \ref{fig:p_pred_heatmap_alt} bottom left), the general conclusion would be that (logged) competition increases mortality as predicted closing chance is highest in areas of low population and large private museum populations.
However, using audience (models 4 and 5, figure \ref{fig:p_pred_heatmap_alt} bottom right) leads to the opposite conclusion, as higher audience is associated with higher mortality; predicted closing chance is highest for areas of low numbers of private museums and large populations.
While it is beyond the scope of the paper to explore the origin of these diverging perspectives in detail, it is worth pointing out that the main specification of private interacted private museum and population counts captures both of these relationships, which arguably makes it preferable for its encompassingness.
\subsection*{Alternative sample specifications}
\label{sec:org9b637b1}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:39 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lllll}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_onlycryside} & \multicolumn{1}{l}{r\_wocryside} & \multicolumn{1}{l}{r\_pop42}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & $-.04 \; (0.34)$ & $-1.07 \; (0.78)$ & $.21 \; (0.44)$ & $-.01 \; (0.34)$ \\ 
   & Gender - Couple & $-.14 \; (0.32)$ & $-.27 \; (0.46)$ & $.07 \; (0.52)$ & $-.12 \; (0.32)$ \\ 
   & Founder died & $.28 \; (0.43)$ & $.58 \; (0.59)$ & $-.19 \; (0.77)$ & $.29 \; (0.43)$ \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & $.20 \; (0.41)$ & $.31 \; (0.58)$ & $1.02 \; (0.65)$ & $.18 \; (0.41)$ \\ 
   & Self-Identification - Collection & $-.45 \; (0.54)$ & $-18.23 \; (4781.88)$ & $.95 \; (0.71)$ & $-.50 \; (0.55)$ \\ 
   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ & $.67 \; (0.46)$ & $1.95 \; (0.51)^{***}$ & $1.09 \; (0.31)^{***}$ \\ 
   & AN Ranking - Included & $.19 \; (0.34)$ & $.55 \; (0.58)$ & $-.32 \; (0.48)$ & $.18 \; (0.34)$ \\ 
   & AN Ranking - Dropped & $.46 \; (0.50)$ & $-.06 \; (0.85)$ & $.18 \; (0.73)$ & $.47 \; (0.50)$ \\ 
   & Founder name in Museum name & $.05 \; (0.28)$ & $.24 \; (0.44)$ & $-.30 \; (0.42)$ & $.04 \; (0.28)$ \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & $.65 \; (0.34)$ & $.88 \; (0.44)^{*}$ & $-1.16 \; (2.52)$ & $.67 \; (0.34)^{*}$ \\ 
   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ & $-.04 \; (0.02)$ & $1.33 \; (2.38)$ & $-.03 \; (0.02)$ \\ 
   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ & $1.69 \; (0.81)^{*}$ & $.17 \; (0.17)$ & $.20 \; (0.12)$ \\ 
   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ & $.64 \; (1.06)$ & $.19 \; (0.10)$ & $.22 \; (0.20)$ \\ 
   & Nbr PM$^{2}$ within 10km & $NA$ & $NA$ & $NA$ & $.01 \; (0.02)$ \\ 
   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ & $-.54 \; (1.83)$ & $-.07 \; (0.04)^{*}$ & $-.02 \; (0.09)$ \\ 
   & Nbr PM$^{2}$ (10km) * Pop (10km) & $NA$ & $NA$ & $NA$ & $-.01 \; (0.01)$ \\ 
   & Great Recession (2008/09) & $-1.59 \; (1.01)$ & $-.75 \; (1.04)$ & $-18.42 \; (5245.29)$ & $-1.59 \; (1.01)$ \\ 
   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ & $.46 \; (0.47)$ & $.30 \; (0.41)$ & $.45 \; (0.29)$ \\ 
   \hline
 & Museums & $503$ & $283$ & $219$ & $503$ \\ 
   & Museum-years & $6096$ & $3311$ & $2265$ & $6096$ \\ 
   & Closures & $68$ & $28$ & $35$ & $68$ \\ 
   & log. Likelihood & $-339.68$ & $-116.47$ & $-139.36$ & $-338.79$ \\ 
   & AIC & $711.35$ & $264.94$ & $310.72$ & $713.59$ \\ 
   & BIC & $746.87$ & $286.25$ & $335.60$ & $753.54$ \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH models of different local density specifications} 
\label{tbl:t_reg_coxph_density}
\end{table}

To investigate the robustness of the coefficients across different values, table \ref{tbl:t_reg_coxph_density} shows how coefficients according to sample restrictions. 
In model 1, only museums are included which are located in areas with the highest value combination of number and private museums and population, i.e. museums located in an environment of less than 2 million people and 0 or 1 other private museums (the "countryside").
In model 2, the "countryside" is excluded.
However, both these models are not reliable, as they do not properly converge (indicated by extremely large coefficients in both models).
\subsection*{Alternative time range specifications}
\label{sec:org68f7010}
% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lllll}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_2005} & \multicolumn{1}{l}{r\_2010} & \multicolumn{1}{l}{r\_2015}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & $-.04 \; (0.34)$ & $.00 \; (0.34)$ & $.05 \; (0.34)$ & $.31 \; (0.37)$ \\ 
   & Gender - Couple & $-.14 \; (0.32)$ & $-.10 \; (0.32)$ & $-.39 \; (0.35)$ & $-.35 \; (0.40)$ \\ 
   & Founder died & $.28 \; (0.43)$ & $.13 \; (0.46)$ & $.34 \; (0.46)$ & $-.22 \; (0.55)$ \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & $.20 \; (0.41)$ & $.25 \; (0.42)$ & $.24 \; (0.43)$ & $-.13 \; (0.48)$ \\ 
   & Self-Identification - Collection & $-.45 \; (0.54)$ & $-.41 \; (0.54)$ & $-.37 \; (0.55)$ & $-.62 \; (0.60)$ \\ 
   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ & $1.14 \; (0.31)^{***}$ & $1.15 \; (0.32)^{***}$ & $.96 \; (0.35)^{**}$ \\ 
   & AN Ranking - Included & $.19 \; (0.34)$ & $.17 \; (0.34)$ & $.26 \; (0.35)$ & $-.35 \; (0.49)$ \\ 
   & AN Ranking - Dropped & $.46 \; (0.50)$ & $.22 \; (0.55)$ & $.28 \; (0.55)$ & $.13 \; (0.56)$ \\ 
   & Founder name in Museum name & $.05 \; (0.28)$ & $.05 \; (0.28)$ & $-.01 \; (0.29)$ & $.46 \; (0.32)$ \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & $.65 \; (0.34)$ & $.70 \; (0.38)$ & $.40 \; (0.45)$ & $.25 \; (0.51)$ \\ 
   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ & $-.03 \; (0.02)$ & $-.02 \; (0.03)$ & $-.02 \; (0.06)$ \\ 
   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ & $.27 \; (0.10)^{**}$ & $.25 \; (0.10)^{**}$ & $.24 \; (0.11)^{*}$ \\ 
   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ & $.25 \; (0.08)^{***}$ & $.25 \; (0.08)^{***}$ & $.23 \; (0.08)^{**}$ \\ 
   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ & $-.09 \; (0.03)^{**}$ & $-.09 \; (0.03)^{**}$ & $-.07 \; (0.03)^{*}$ \\ 
   & Great Recession (2008/09) & $-1.59 \; (1.01)$ & $-1.69 \; (1.01)$ & $NA$ & $NA$ \\ 
   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ & $.33 \; (0.29)$ & $.28 \; (0.30)$ & $.12 \; (0.31)$ \\ 
   \hline
 & Museums & $503$ & $502$ & $499$ & $485$ \\ 
   & Museum-years & $6096$ & $5483$ & $4474$ & $2901$ \\ 
   & Closures & $68$ & $67$ & $64$ & $50$ \\ 
   & log. Likelihood & $-339.68$ & $-329.47$ & $-304.28$ & $-217.32$ \\ 
   & AIC & $711.35$ & $690.94$ & $638.57$ & $464.65$ \\ 
   & BIC & $746.87$ & $726.22$ & $670.95$ & $493.33$ \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH regression results with different time slices} 
\label{tbl:t_reg_coxph_timeslice}
\end{table}

Table \ref{tbl:t_reg_coxph_timeslice} investigates whether relationships have substantially changed over time.
However, subsetting the dataset to different year ranges shows general consistency of the main findings, in particular insignificant coefficients for the founder's death, gender, Artnews ranking variables, inclusion of founder name in museum name, positive and significant coefficients for self-identification as other, population and private museum numbers, and a significant negative interaction between private museum numbers and population.
\subsection*{Inclusion of Exhibition data}
\label{sec:org3423df8}
